The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-11 analysis/paper/paper.qmd

# Read thesis metadata ----
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

# TODO replace the following lines with the metadata included in the package
# emu_metadata <- data(emu_metadata)
## Read metadata for all theses
all_theses <- read_xlsx(path = here(data_path, "theses-all.xlsx"))

## Read only metadata for theses with PDF available
emu <- read_csv(here(data_path, "theses-metadata.csv")) |>
  mutate(text_raw = "") |>
  filter(!is.na(pdf_via))

# TODO replace this and next code chunk with reading `text_raw` from the package
# emu <- data(emu_raw)
pdf_paths <- here(data_path, emu$file_name)
```

@@

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text_and_location.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu$text_raw <- convert_pdf_text(pdf_paths)

  # Add latitude and longitude information to theses data frame
  emu <- geocode_thesis_locations(emu)

  # Write thesis dataframe to file
  write_csv(emu, data_path)
} else {
  emu$text_raw <- read_csv(data_path)$text
  emu$longitude <- read_csv(data_path)$longitude
  emu$latitude <- read_csv(data_path)$latitude
}

@@

emu$text_clean <- emu$text |>
  clean_basic()

@@

```{r ngrams}
#| dependson: clean-text

## Bigrams
emu_bigrams <- emu |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", lemma = TRUE) |> 
  unite(ngram_lemma, w_1_lemma, w_2_lemma, sep = "_", remove = FALSE)

bigram_counts <- emu_bigrams |> 
  count(ngram, sort = TRUE) |> 
  filter(n > 20)

emu_bigrams <- emu_bigrams |> 
  filter(ngram %in% bigram_counts$ngram)

bigram_lemma_counts <- emu_bigrams |> 
  count(w_1_lemma, w_2_lemma, sort = TRUE) |> 
  filter(n > 5)

# Concatenate bigrams

# # First attempt using a named vector in `str_replace_all()`
c_bigrams <- paste(emu_bigrams$ngram_lemma, sep = "_")
names(c_bigrams) <- emu_bigrams$ngram

system.time(
  emu$text_clean <- emu$text_clean |>
    str_replace_all(fixed(c_bigrams))
)

# Second attempt with `mgsub::mgsub()`
# emu$text_clean <- mgsub(emu$text_clean,
#                         pattern = emu_bigrams$ngram,
#                         replacement = emu_bigrams$ngram_lemma)

## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text_clean", lemma = TRUE)

@@

trigram_lemma_counts <- emu_trigrams |> 
  count(w_1_lemma, w_2_lemma, w_3_lemma, sort = TRUE)

```{r}
## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf
```

```{r}
## Trigram tf-idf
trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

trigram_tf_idf
```

```{r}
## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()

>>>>

@@

# Read thesis metadata ----
data(emu_metadata)

# Load the raw text dataset 
data(emu_raw)

# Join  text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")

@@

emu$text_clean <- emu$text_raw |>
  clean_basic()

@@

```{r}
#| label: ngrams
#| dependson: clean-text

## Bigrams
emu_bigrams <- emu |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

bigram_counts <- emu_bigrams |> 
  count(w_1, w_2, sort = TRUE)

bigram_stem_counts <- emu_bigrams |> 
  count(w_1_stem, w_2_stem, sort = TRUE)

bigram_counts
bigram_stem_counts
```

```{r}
## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text")

@@

trigram_counts

## Bigram tf-idf
bigram_tf_idf <- emu_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

bigram_tf_idf

## Trigram tf-idf
trigram_tf_idf <- emu_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

trigram_tf_idf

## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()
